|

### 2020-03-24 inst/manuscript/candidaev_figures.Rmd
Update affiliation in figures pdf

---
title: | 
   **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
   family proteins**
author: | 
   | Charlotte Dawson^a^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
     Pierre Faou^b^,
   | Mark Bleackley^a^, Marilyn Anderson^a^
date: | 
   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
     Molecular Science, La Trobe University, 
     Melbourne, 3086, Victoria, Australia*
   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
     Molecular Science, La Trobe University, Melbourne, 
     3086, Victoria, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/taylor-and-francis-acs.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

@@

# generate volcano plot
f2b1 <- plot_volcano(data = yeast_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     use_labels = TRUE,
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", 
                                 "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig"), 
                      name = element_blank()) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 Y')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('101')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('117')", parse = TRUE, 
           colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('276')", parse = TRUE, 
           colour = unname(ev_pal[1]))
```

@@

# generate volcano plot
f2b4 <- plot_volcano(data = biofilm_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     use_labels = TRUE, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig")) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('105')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('100')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('453')", 
           parse = TRUE, colour = unname(ev_pal[1]))

>>>>

---
title: | 
   **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
   family proteins**
author: | 
   | Charlotte Dawson^ac^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
     Pierre Faou^b^,
   | Mark Bleackley^a^, Marilyn Anderson^a^
date: | 
   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
     Molecular Science, La Trobe University, 
     Melbourne, 3086, Victoria, Australia*
   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
     Molecular Science, La Trobe University, Melbourne, 
     3086, Victoria, Australia*
   | *^c^Cambridge Centre for Proteomics, Milner Therapeutics Institute, 
     Jeffrey Cheah Biomedical Centre, University of Cambridge, 
     Puddicombe Way, Cambridge CB2 0AW, United Kingdom*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/taylor-and-francis-acs.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

@@

# generate volcano plot
f2b1 <- plot_volcano(data = yeast_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     use_labels = TRUE,
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", 
                                 "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,3,1)]), 
                      breaks = c("EV up", "WCL up", "not sig"), 
                      name = element_blank()) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 Y')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('101')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('117')", parse = TRUE, 
           colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('276')", parse = TRUE, 
           colour = unname(ev_pal[1]))
```

@@

# generate volcano plot
f2b4 <- plot_volcano(data = biofilm_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     use_labels = TRUE, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,3,1)]), 
                      breaks = c("EV up", "WCL up", "not sig")) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('105')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('100')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('453')", 
           parse = TRUE, colour = unname(ev_pal[1]))
